Grappa: Scalable Computing on Commodity Hardware \\for Irregular Applications

### 2012-07-23 doc/asplos13/conclude.tex
c

We explored the performance of Grappa on three algorithms: unbalanced tree
search, breadth first search, and betweenness centrality. Performance
comparisons to the Cray XMT for a small number of nodes (16 nodes / 96 cores)
show great promise: Grappa performs on-par with the far more expensive and
custom XMT system, sometimes achieving better performance and sometimes worse.
Our initial scaling experiments to a higher number of nodes suggests Grappa
does scale, but there is some room for further improvement. Due to limitations
in the initial aggregator design Grappa cannot utilize more than 6 cores/node,
and this limits not only peak performance at a small number of nodes, but
scaling performance at a larger number of nodes. Current work is ongoing on a
new aggregator design.

>>>>

We explored the performance of Grappa on three algorithms: unbalanced tree
search, breadth first search, and betweenness centrality. Performance
comparisons to the Cray XMT for a small number of nodes (16 nodes / 96 cores)
show great promise: Grappa performs on-par with the far more expensive and
custom XMT system, sometimes achieving better performance and sometimes worse.
Our initial large scaling experiments to a higher number of nodes shows both promise and room for improvement.  Grappa trounces XMT on UTS, but has a ways to go with achieving the same scaling performance on betweenness centrality.  Grappa and XMT scale at similar rates on BFS, a key benchmark in this space.
